\TheTitle

### 2017-07-07 paper/lineval.tex
many comments

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage[hyphens]{url}
\urlstyle{same}

@@

%% Table Support
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{tabulary}

@@

%% Tikz
\usetikzlibrary{positioning, arrows}

@@

@@

In this section, we describe the methods used to for designing and
implementing the user study.

@@

@@

@@

The third task set is purely qualitative, to gain better understanding
of whether participants preferred working with the \mt model in \tool,
or working with the DAG in Gitk, and what aspects they preferred from
each tool. The final group of questions is simply to gain a better
understanding of the demographic of our participants.

@@

@@

@@

The summarization tasks (Table~\ref{tab:summarization_tasks}) are
grouped into task sets by theme. The tasks within the task set are
shuffled, and the task sets are shuffled, to ensure that similar
questions are together, but not in the same order, and to ensure that
the themes are in randomized order between participants. The order of
the commits is shuffled, as well. The order of the tool is randomized,
choosing to start with either \tool or Gitk, to ensure that we do not
place a bias on one tool through the experiment.

@@

Finally, we ask the user for their opinions on the tools and for some
information about their level of experience with git. This portion of
the study is qualitative and does not rely on either of the tool,
instead attempting to determine which model provided the user with a
better experience.

We do not shuffle the questions in this set of questions, as this should
not have an impact on the opinions of the participant at this point.
These questions are designed to provide us with a better understanding
of preference, and insight on why, the participant had that preference.

We ask the following questions in this order;

@@

The last three questions in this section are aimed at getting a better
understanding of the demographic of our participants.

@@

@@

@@

We use the \tool database, containing commits and merge-tree information
from April 16th 2005 to October 14th, 2014, which corresponds to being
between Linux release 2.6.12-rc3 and Linux 3.17-rc1. \evan{Cite the
  database even more?} We chose the commits based on tree sizes. We
found that a majority of the trees contain at most seven inner commits,
while more than 25\% of the trees contain a single commit. 75\% of the
tree contained up to 51 inner commits and merges, and finally the
largest tree contained 7217 nodes. We chose to work with the trees in
the first and second quartile, as merge trees of sizes between one and
seven, not including the merge into the master branch, make up the
majority of the trees in the database.

From here, we selected one tree from the trees of a single commit at
random. Selecting a commit from that tree is trivial, as there is only
one to choose.

We selected one tree of size seven at random from all trees of size
seven. We placed a restriction the trees, the selected tree must include
at least one internal merge to increase the complexity of the trees
tested. After randomly selecting a tree, we chose in internal commit at
random, using the \verb|random.choice| function in python 3.6.1.

@@

\begin{figure}[bpt]
  \centering
  \includegraphics[width=0.08\linewidth]{figures/commits/1-commit.pdf}
  \caption{The first merge tree used in the user study, a merge tree
    containing a single commit}
  \label{fig:commit_1}
\end{figure}

\begin{figure}[bpt]
  \centering
  \includegraphics[width=0.5\linewidth]{figures/commits/7-commits.pdf}
  \caption{The second merge tree used in the user study, a merge tree
    containing seven commits}
  \label{fig:commit_2}
\end{figure}

@@

We recorded the audio and screen capture video for each participant in
the study for further analysis. After capturing the information, we
extracted various metrics from the videos. From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy. Correctness is a binary
value, it is true if the response was correct and false if the response
was incorrect. The accuracy is measures in distance from the correct
value. An accuracy of zero indicates a correct answer. All tasks in the
summarization tasks include an accuracy metric except T7, which will
only be right or wrong, and therefore cannot meaningfully be measured by
a distance.

@@

In Table~\ref{tab:conceptual_results}, we are able to see an overview of
the results from the conceptual questions.

\begin{table*}[htpb]
  \centering
  \caption{Results from the conceptual questions}
  \label{tab:conceptual_results}
  \begin{tabular}{ll|r|lrr|rrr}
    Question                      & Commit & Answer & Median & Mean  & Variance & Median(s) & Mean(s) & Variance(s)\\\hline\hline
    Number of commits in the tree & \comA  & 1      & 4      & 19.11 & 753.11   & 10.0      & 49.92   & 5952.08\\
    Number of merges in the tree  & \comA  & 1      & 5      & 8.27  & 53.62    & 7.5       & 24.67   & 884.42\\\hline
    Number of commits in the tree & \comB  & 5      & 4      & 7.80  & 136.84   & 31.5      & 106.83  & 54123.42\\
    Number of merges in the tree  & \comB  & 3      & 3.5    & 5.40  & 50.27    & 11.0      & 65.6    & 29798.82\\
  \end{tabular}
\end{table*}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\urlstyle{same}

@@

%% Table Support
\usepackage{array}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{tabulary}

@@

\usetikzlibrary{positioning, arrows}

@@

\dmg{start by describing what you mean by user study... to evaluate linvis we performed a user study...}

\dmg{and you are evaluating the visualizations, NOT the DAG}

@@

In this section, we describe the methods used to for designing and
implementing the user study.
\dmg{no, you describe the study, which includes the methods}

\dmg{Start by giving an overall overview of the study: the study consists of a set of tasks that users are expected to
  perform... do a top down description of what users will do
}

@@

\dmg{use tasks, not questions. you are asking them to do something that requires an answer, that is different than a question}

@@

\dmg{avoid editorializing your text: remove purely}

\dmg{watch for tense... we don't beging... the tasks begin... or better, the first tasks...}

@@

The third task set is purely qualitative, \dmg{and are their goal is ... don't imply content in your sentences... be
  precise; this applies to the paragraph before} to gain better understanding
of whether participants preferred working with the \mt model in \tool,
or working with the DAG in Gitk, and what aspects they preferred from
each tool. The final group of questions is simply to gain a better
understanding of the demographic of our participants.

@@

\dmg{given the choice, not allowed. 
  I don't understand this section.
  You need to be more top-down in your description. you need to provide context on what the
  users are expected to do, and why. So what are the tasks? You never explain.
what is the goal of the tasks? how many? 
what were the tasks? what is expected from each? you need to answer these questions, not necessarily in the same order.
also, remember this is a comparative study, so I presume the users were asked to do both with linvis and without it
(choice of gitk/git command line)
}

@@

\dmg{I don't like the present tense, but that is your option}

@@

\dmg{again, you are going into details first. First the tasks --see above--
  including their grouping.
  then at the end, describe the randomization and why it is done (which you did)
}

The summarization tasks (Table~\ref{tab:summarization_tasks}) are
grouped into \dmg{how many?} set of tasks according to their theme. The tasks within a given task set are
shuffled, and the task sets are shuffled, to ensure that similar
questions are together, but not in the same order, and to ensure that
the themes are in randomized order between participants. The order of
the commits is shuffled, as well. The order of the tool is randomized,
choosing to start with either \tool or Gitk, to ensure that we do not
place a bias on one tool through the experiment.

@@

Finally, we ask the user for their opinions on the tools and for some
information about their level of experience with git.
\dmg{be more precise: understanding or preference is too broad. What you want to know 
answers to specific questions regarding how the tools compare and which ones they would prefer}
The first three questions are intended to provide us with a better understanding
of preference, and insight on why, the participant had that preference.  
The last three questions in this section are aimed at getting a better
understanding of the demographic of our participants.

@@

@@

\dmg{tell me first why you need to create a script, so I know what you do something:
we did random assignment of tasks (explain what you did) and randomized the order in which the tasks were performed.
 Then explain why you need a script}

\dmg{it does not randomize the order the tools. It randomizes which tool is going to be used on each tasks.
be precise with your language}

\dmg{what you explained how commits relate to tasks and how they get assigned? think as if you are explaining this to
  somebody who has to do this: you are the designer, explaining the why and the how }

@@

\dmg{see my comments in previous section. it is ok to explain them here, but you need to explain what they are briefly
  in the previous section}

@@

\dmg{this place does not require a description of the database. This requires just to say
the commits/merge set (dates and numbers are ok) only}
We use the \tool database, containing commits and merge-tree information
from April 16th 2005 to October 14th, 2014, which corresponds to being
between Linux release 2.6.12-rc3 and Linux 3.17-rc1. \evan{Cite the
  database even more?}
\dmg{again, i have problems with your writing: ``we wanted to use in the study commits of different size, to determine
  if the size had an impact in the completion of the tasks. We chose commits of three different sizes...}
We chose the commits based on tree sizes. We
\dmg{we didn't find: this is a fact, not a discovery; what is a majority? 50\%+1? be precise}
\dmg{drop the word inner, and do it in order: 25\% of trees have only one commit, 50\%.., 75\%...}
found that a majority of the trees contain at most seven inner commits,
while more than 25\% of the trees contain a single commit. 75\% of the
tree contained up to 51 inner commits and merges, and finally the
largest tree contained 7217 nodes. We chose to work with the trees in
\dmg{if you are going to use the words quartile, just use them before in your description eg: the distribution of the
  sizes of the trees is x, y merges, whose size corresponded to the 25 ,50 quartiles, simple and precisee}
the first and second quartile, as merge trees of sizes between one and
seven, not including the merge into the master branch, make up the
majority of the trees in the database.

\dmg{remove from here, what is here? this is not a road trip :)}
From here, we selected one tree from the trees of a single commit at
random. Selecting a commit from that tree is trivial, as there is only
one to choose.\dmg{remove the obvious, instead concentrate on why the others are not trivial}

We selected one tree of size seven at random from all trees of size
seven\dmg{how many where there?}. We placed a restriction the trees, the selected tree must include
at least one internal merge to increase the complexity of the trees
tested. For each randomly selecting a tree, we chose one of its internal commits at
random (using the \verb|random.choice| function in python 3.6.1).

\dmg{question: so you chose only one commit of each size, and the randomization was which tool to use
for each question? or did they have to do the same task for two commits?}

@@

\begin{figure}[bpt]
  \centering
\begin{tabular}{ m{1.5cm} m{3cm} }
  \includegraphics[height=0.5in]{figures/commits/1-commit.pdf} &
  \includegraphics[height=1in]{figures/commits/7-commits.pdf}\\
\end{tabular}
  \caption{The merge trees used in the user study, 
    containing one and seven commits, respectively.}
  \label{fig:commit_1}
\end{figure}

@@

\dmg{this is still methodology.}

We recorded the audio and screen capture video for each participant in
the study for further analysis.
\dmg{you don't need this sentence, it is redundant}
After capturing the information, we
extracted various metrics from the videos.
\dmg{ you don't record, you measure}
From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy.
\dmg{and then somethings you are over precise :): correctness is simply whether their answer to the task was correct or not}
Correctness is a binary
value, it is true if the response was correct and false if the response
was incorrect.
\dmg{if you are going to use this metric, you need to define precisely. remember, you are giving this to somebody else
  to implement}
The accuracy is measures in distance from the correct
value. An accuracy of zero indicates a correct answer. All tasks in the
summarization tasks include an accuracy metric except T7, which will
only be right or wrong, and therefore cannot meaningfully be measured by
a distance.

@@

\dmg{i don't like the expression: we are able to see... too long.. be to the point: Table X shows/depicts/ etc ... they
  are not overviews, they are a summary}
In Table~\ref{tab:conceptual_results}, we are able to see an overview of
the results from the conceptual questions.

\begin{table*}[htpb]
  \centering
  \caption{Results from the conceptual questions\dmg{what are the columns? they need captions}}
  \label{tab:conceptual_results}
  \begin{tabular}{ll|r|lrr|rrr}
    Question                      & Commit & Answer & Median & Mean  & Variance & Median(s) & Mean(s) & Variance(s)\\\hline\hline
    Number of commits in the tree & \comA  & 1      & 4      & 19.11 & 753.11   & 10.0      & 49.92   & 5952.08\\
    Number of merges in the tree  & \comA  & 1      & 5      & 8.27  & 53.62    & 7.5       & 24.67   & 884.42\\\hline
    Number of commits in the tree & \comB  & 5      & 4      & 7.80  & 136.84   & 31.5      & 106.83  & 54123.42\\
    Number of merges in the tree  & \comB  & 3      & 3.5    & 5.40  & 50.27    & 11.0      & 65.6    & 29798.82\\
  \end{tabular}
\end{table*}
